Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-05 paper/Introduction.tex
Cut out text

\adamc{I don't understand what this paragraph is saying.}
From a methodological perspective, this two-step process leaves much
to be desired. The significant effort of
verification is effectively lost by the concurrent non-trivial tasks
of translation from the protocol representation to a hardware
description and the necessary refinement to add missing implementation
details to the protocol.

Verified protocols are often described via Term Rewrite
Systems (TRS) \adamc{citation for TRSes?}, which apply equational logic to describe systems at an
interesting point on the spectrum between declarative and operational methods.
It was shown by Dave
\etal{}~\cite{DNA:CoherenceImplementation} that such a verified
protocol could be transliterated into Bluespec~\cite{Bluespec:TFRG}, a
hardware description language based on Guarded Atomic Actions, a
restriction of TRS~\cite{Hoe:TCAD}. In this way one reduces the correctness of
the implementation to the correctness of the protocol, with no need
for separate reasoning about an implementation. While the current Bluespec compiler
does not support some implementation elements that are common in practice
(\eg{} fairness guarantees, atomic actions running over multiple clock cycles),
recent work has provided key insights toward lifting the
restrictions~\cite{DNA:CoherenceImplementation, Karczmarek}.  We
believe that Bluespec and its future evolutions represent a
very promising platform for productive implementation and
verification of hardware components, including cache-coherent
shared memories.

>>>>

Methodologically, this process is flawed. The guarantees gained from
verifying the protocol have no bearing on the implementation if
hardware designers must do a manual translation to RTL.

Verified protocols are often described via Term Rewrite Systems (TRS),
which apply equational logic to describe systems at an interesting
point on the spectrum between declarative and operational methods.  It
was shown by Dave \etal{}~\cite{DNA:CoherenceImplementation} that such
a verified protocol could be transliterated into
Bluespec~\cite{Bluespec:TFRG}, a hardware description language based
on Guarded Atomic Actions, a restriction of TRS~\cite{Hoe:TCAD}. In
this way one reduces the correctness of the implementation to the
correctness of the protocol, with no need for separate reasoning about
an implementation. While the current Bluespec compiler does not
support some implementation elements that are common in practice
(\eg{} fairness guarantees, atomic actions running over multiple clock
cycles), recent work has provided key insights toward lifting the
restrictions~\cite{DNA:CoherenceImplementation, Karczmarek}.  We
believe that Bluespec and its future evolutions represent a very
promising platform for productive implementation and verification of
hardware components, including cache-coherent shared memories.

### 2014-02-05 paper/System.tex
Cut out text

Input and output happens at the leaves in the form of memory requests
issued from and responses issued to the associated processor. These will be
represented by two mappings, one from $\mathbb{N}$ to requests and the other
from $\mathbb{N}$ to responses. For each leaf $c$, $c.\pos$ represents the
position of the next request to process; it is set to $0$ initially.
\adamc{What is a ``position'' here?  Is ``sequence number'' a better choice?}
\adamc{I hope the diagram explains what these mappings mean, and in general what
the tree structure really means.}

@@

%Of course, all these invariants have to be enforced by the protocol.

>>>>

Input and output happens at the leaves in the form of a stream of
memory requests issued from and responses issued to the associated
processor. These will be represented in Coq as two mappings each with
integer ($c.\pos$) indicating how many elements in the stream we have
handled so far.

%% \adamc{What is a ``position'' here?  Is ``sequence number'' a better choice?}
%% \adamc{I hope the diagram explains what these mappings mean, and in general what
%% the tree structure really means.}

@@
